### 2018-04-26 doc/paper.tex
Adding note about asymptotic behavior of flop counts.
Also adding a note about when the Horner count applies.
Added some base algorithm blocks.

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}

@@

@@

After implementing for \(K = 2, 3, \ldots, 12\) and instrumenting all
relevant floating point operations, the \(K\)-fold Horner requires
\[(5 \cdot 2^K - 8)n + \left((K + 8) 2^K - 12K - 6\right)\]
flops to evaluate a degree \(n\) polynomial. As a comparison, the
non-compensated form of Horner requires \(2n\) flops. Of these,
\(\left(2^{K - 1} - 1\right)n - 2^{K - 1}(K - 3) - 2\) are
FMA (fused-multiply-add) instructions.

After implementing for \(K = 2, 3, 4, 5\) and instrumenting all relevant
floating point operations, the \(K\)-fold de Casteljau requires
\[(15K^2 - 34K + 26)T_n + K + 5\]
flops to evaluate a degree \(n\) polynomial. (Here \(T_n\) is the
\(n\)th triangular number.) As a comparison, the non-compensated form of
de Casteljau requires \(3 T_n + 1\) flops. Of these, \((3K - 4)T_n\) are
FMA instructions. On hardware that doesn't support FMA,
every FMA will be exchanged for 10 \(\ominus\)'s and 6 \(\otimes\)'s so the
count will increase by \((10 + 6 - 1)(3K - 4)T_n\).

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/215651/32270
\usepackage[ruled]{algorithm2e}

@@

\section{IEEE Stuff}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoSum}(a, b)\) \\
  \quad \(x = a \oplus b\) \\
  \quad \(z = x \ominus a\) \\
  \quad \(y = (a \ominus (x \ominus z)) \oplus (b \ominus z)\)

  \caption{\textit{EFT of the sum of two floating point numbers.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{Split}(a)\) \\
  \quad \(z = a \otimes (2^r + 1)\) \\
  \quad \(x = z \ominus (z \ominus a)\) \\
  \quad \(y = a \ominus x\)

  \caption{\textit{Splitting of a floating point number into two parts.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoProd}(a, b)\) \\
  \quad \(x = a \otimes b\) \\
  \quad \(\left[a_h, a_l\right] = \mathtt{Split}(a)\) \\
  \quad \(\left[b_h, b_l\right] = \mathtt{Split}(b)\) \\
  \quad \(y = a_l \otimes b_l \ominus (((x \ominus a_h \otimes b_h)
      \ominus a_l \otimes b_h) \ominus a_h \otimes b_l)\)

  \caption{\textit{EFT of the product of two floating point numbers.}}
\end{algorithm}

\begin{algorithm}[H]
  \textit{function} \(\left[x, y\right] = \mathtt{TwoProdFMA}(a, b)\) \\
  \quad \(x = a \otimes b\) \\
  \quad \(y = \mathtt{FMA}(a, b, -x)\)

  \caption{\textit{EFT of the sum of two floating point numbers with a FMA.}}
\end{algorithm}

@@

After implementing for \(K = 2, 3, \ldots, 12\) and instrumenting all
relevant floating point operations, the \(K\)-fold Horner requires
\[(5 \cdot 2^K - 8)n + \left((K + 8) 2^K - 12K - 6\right) =
\mathcal{O}\left((n + K)2^K\right)\]
flops to evaluate a degree \(n\) polynomial (this only applies when
\(n \geq K - 1\)). As a comparison, the
non-compensated form of Horner requires \(2n\) flops. Of these,
\(\left(2^{K - 1} - 1\right)n - 2^{K - 1}(K - 3) - 2\) are
FMA (fused-multiply-add) instructions.

After implementing for \(K = 2, 3, 4, 5\) and instrumenting all relevant
floating point operations, the \(K\)-fold de Casteljau requires
\[(15K^2 - 34K + 26)T_n + K + 5 =
\mathcal{O}\left(n^2 K^2\right)\]
flops to evaluate a degree \(n\) polynomial. (Here \(T_n\) is the
\(n\)th triangular number.) As a comparison, the non-compensated form of
de Casteljau requires \(3 T_n + 1\) flops. Of these, \((3K - 4)T_n\) are
FMA instructions. On hardware that doesn't support FMA,
every FMA will be exchanged for 10 \(\ominus\)'s and 6 \(\otimes\)'s so the
count will increase by \((10 + 6 - 1)(3K - 4)T_n\).
